Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-07 paper.tex
Create anonymisation files
Doctor Who theme - sorry!

\title{Does Anybody Really Know What Time It Is?\\
Automating the Extraction of Date Scalars}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% ``name/affiliations'' may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Richard Wesley \\
%       \affaddr{Tableau Software}\\
%       \affaddr{837 North 34th Street}\\
%       \affaddr{Seattle, WA 98103}\\
%      \email{hawkfish@tableau.com}
% 2nd. author
\alignauthor
Vidya Setlur\\
%       \affaddr{Tableau Software}\\
 %      \affaddr{837 North 34th Street}\\
%       \affaddr{Seattle, WA 98103}\\
 %      \email{vsetlur@tableau.com}
% 3rd. author
\alignauthor
Dan Cory\\
%       \affaddr{Tableau Software}\\
%       \affaddr{837 North 34th Street}\\
%       \affaddr{Seattle, WA 98103}\\
%       \email{dcory@tableau.com}
%       \email{\{hawkfish,vsetlur,dcory\}@tableau.com}
\sharedaffiliation
       \affaddr{Tableau Software}\\
       \affaddr{837 North 34th Street}\\
       \affaddr{Seattle, WA 98103}\\
       \email{\{hawkfish,vsetlur,dcory\}@tableau.com}
}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
We would like to thank to Pat Hanrahan for encouraging this work; Roger Hau for providing the resources to productize it; and Jason King, whose harrowing live demonstration of manual \dateparse in front of several thousand people inspired this project.

>>>>

\title{Does Anybody Really Know What Time It Is?\\
Automating the Extraction of Date Scalars}
\input{anonymous}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
\input{credits}
